---
title: "metric_graph"
author: "Olivia Freides"
date: "10/27/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages(c("tidyverse","igraph","tidygraph"))
library(tidyverse)
library(igraph)
library(tidygraph) # tiidygraph has a lot of wrapper on igraph measures, but has a few of its own.
```

## Metric Graph:

GOAL:
Compute graph whose edges are 
(i, i+1) if d(pulse i, pulse i_1) < threshold
and
(zero vector, i) if d(0, pulse i) < threshold 
```{r}
pulse <- as.data.frame(matrix(complex(real = rnorm(100, sd = 0.5),
                                      imaginary = rnorm(100, sd = 0.1)),
                              nrow = 10))
```

```{r}
euclidean_dist <- function(x, y) sqrt(sum(abs((x - y)^2)))
euclidean_norm <- function(x) sqrt(sum(abs((x)^2)))
```

```{r}
pulse %>%
c-> eudist
```

Function for eudist
```{r}
eu_dist_norm <- function(matrix){
  matrix %>%
  pivot_longer(everything()) %>%
  mutate(name = as_factor(name)) %>%
  nest(data = value) %>%
  mutate(datalag = lag(data, n = 1, default = NA), namelag = lag(name, n=1, default = NA)) %>%
  filter(map(datalag, ~!is_empty(.)) %>% unlist) %>%
  mutate(distance = map2(data, datalag, euclidean_dist), 
         norm = map(data, euclidean_norm))
}
```

Compare with VR complex w/ same threshold

Step 1:
Generate a random symmetric matrix of complex values, 1000x1000

Step 4:
Create the distance matrix based on a pre-specified threshold.

```{r}
metrix <- function(matrix, threshold){
  matrix_d <- eu_dist_norm(matrix)
  print(matrix_d)
  
  edge_d <- matrix_d %>% filter(distance<2.1) %>% select(name, namelag)
  edge_n <- matrix_d %>% filter(norm<2.1) %>% select(name) %>% mutate(namelag = "V0")
  
  output <- as.matrix(bind_rows(edge_d, edge_n))
  graph_from_edgelist(output) -> graph
  print(output)
  plot(graph, layout = layout.star, vertex.label.dist=3)
  
}

metrix(pulse, 2.1) -> testeradj
# we have to get it back in to matrix form... :()
```

Step 4?:
Create a graph and iterate to a point where the edges are determined by a threshold and assigned a distance. 
Step 5:
Graph from matrix.

```{r}
G0 <- graph_from_adjacency_matrix(testeradj)

is_connected(G0) 
is.connected(G0, mode = "strong") # TRUE
is.connected(G0, mode = "weak")   # TRUE by default of strong.
is.weighted(G0) # We want True...
```

Edges are determined by the threshold and assigned a distance.

